A comparison of classification algorithms applied to the Adult Database

### 2009-12-09 report/final.tex
Experimental evaluation for c4.5

\documentclass[a4paper]{llncs}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage[utf8]{inputenc}
\usepackage{subfigure}
\usepackage{a4wide}
\usepackage{listings}
\usepackage[hyphens]{url}
\urldef{\mails}\path|{ei05011,ei05028}@fe.up.pt|
\bibliographystyle{splncs}
\begin{document}
\title{A comparison of classification algorithms applied to the Adult Database}
\author{Flávio Cruz \and João Azevedo}
\institute{Faculdade de Engenharia da Universidade do Porto\\
    Rua Dr. Roberto Frias, s/n 4200-465 Porto PORTUGAL\\
    \mails}
\maketitle

@@

Various performance metrics for both classification results will be registered:
error rate, mean absolute error, kappa statistic, etc.

@@

>>>>

\documentclass[a4paper]{llncs}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage[utf8]{inputenc}
\usepackage{subfigure}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{listings}
\usepackage[hyphens]{url}
\urldef{\mails}\path|{ei05011,ei05028}@fe.up.pt|
\bibliographystyle{splncs}
\begin{document}
\title{A comparison of classification algorithms applied to the Adult Database}
\author{Flávio Cruz \and João Azevedo}
\institute{Faculdade de Engenharia da Universidade do Porto\\
    Rua Dr. Roberto Frias, s/n 4200-465 Porto PORTUGAL\\
    \mails}
\maketitle

@@

Performance metrics for both classification results will be registered: error rate and time spent
building the classifier and classifying all the examples.

@@

This section shows performance results for the various algorithms.

\subsection{C4.5}

C4.5 in Weka provides a number of parameters to tune the algorithm.
One of these parameters allows the creation of unpruned trees $<$\textbf{-U}$>$.
For pruned trees we can use the confidence threshold parameter that dictates how
much pruning the algorithm will do $<$\textbf{-C float}$>$.

We executed the algorithm using different combinations of the parameters described above.
Table \ref{tbl:results_c45} displays the obtained results. From the table
we note that once the confidence threshold reaches a certain level ($\approx$0.55) the results
are very similar for the unpruned classifier and the over-fitting effect starts to get worse,
where the train data gets very good results ($\approx$11.19 error rate) and the test set gets a
large error rate ($\approx$24).

The confidence threshold for best test error rates appears to be in the interval 0.05-0.15.

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c |}
    \hline
    \textbf{Parameters} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    -U & 11.18 & 23.74 & 0m24.378s \\ \hline
    -C 0.05 & 15.67 & 22.86 & 0m24.414s \\ \hline
    -C 0.1 & 15.22 & 21.69 & 0m25.417s \\ \hline
    -C 0.15 & 14.85 & 22.25 & 0m25.086s \\ \hline
    -C 0.2 & 14.52 & 22.05 & 0m24.436s \\ \hline
    -C 0.25 & 14.40 & 22.08 & 0m24.628s \\ \hline
    -C 0.3 & 14.17 & 23.26 & 0m24.765s \\ \hline
    -C 0.35 & 13.84 & 22.42 & 0m25.154s \\ \hline
    -C 0.4 & 13.68 & 22.49 & 0m24.325s \\ \hline
    -C 0.45 & 13.26 & 22.43 & 0m25.086s \\ \hline
    -C 0.5 & 12.95 & 22.51 & 0m24.874s \\ \hline
    -C 0.55 & 11.19 & 24.94 & 0m25.899s \\ \hline
    -C 0.6 & 11.19 & 23.94 & 0m26.882s \\ \hline
    -C 0.7 & 11.19 & 23.94 & 0m26.638s \\ \hline
    -C 0.8 & 11.19 & 23.94 & 0m26.818s \\ \hline
    -C 0.9 & 11.19 & 23.94 & 0m26.634s \\ \hline
  \end{tabular}
  \caption{Results for C4.5.}
  \label{tbl:results_c45}
  \end{center}
\end{table}
